---
title: "MABT -- MultiAssay big table experiments"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "Jan 2017"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Infrastructure for Multi-Assay Experiments using Google BigTable}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::pdf_document:
    toc: yes
    number_sections: yes
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction and authentication

It is challenging to authenticate in a non-interactive
setting.  All chunks here are eval=FALSE in the build package, but a PDF will
be made available with a completed run.

Here's a setup.
```{r setup,echo=TRUE,eval=TRUE}
suppressPackageStartupMessages({
library(GoogleGenomics)
})
apik = Sys.getenv("GOOGLE_API_KEY")
authenticate(apiKey=apik)
getBQ2 = function() {
suppressPackageStartupMessages({
library(dplyr)
library(bigrquery)
})
my_billing = "cgc-05-0009" # replace billing info here with your own
src_bigquery("cgc-05-0009", "yriMulti", billing = my_billing)
}
```

```{r demo, eval=TRUE}
suppressPackageStartupMessages({
library(MABT)
})
bq = getBQ2()
bq
bano = 
  RangedBT("cgc-05-0009", bq, 
   "banovichSE_expressionData", 
    "banovichSE_rowRanges")
bano
nrow(bano)
```

# Considerations of the code base in 0.0.0

The current objective is to get some performance metrics
on genomic computing with BigTable/BigQuery.  We are not
using the MultiAssayExperiment framework yet, as there is
considerable detailed programming required to create 
objects compliant with the validating API.

## RangedBT class

We have defined an S4 class RangedBT, to wrap instances
of `tbl_bigquery`.  Two such tables are assumed present,
one for `assay` and one for `rangeData`.  We also
retain information on the Google Compute Platform (GCP) project
name and the number of rows (implicitly equal for both tables).

```{r lkcl}
getClass("RangedBT")
```

The constructor is very simple and does not validate or initialize,
though eventually it should.  It takes as input the project name,
the `src_bigtable` instance, and the table names in the src.
```{r lkco}
RangedBT
methods(class="RangedBT")
```

The `nrow` method is of some interest.
```{r lknr}
getMethod("nrow", "RangedBT")
```

## Next steps

- define a "LabeledBT" class that can manage the sample data,
and will answer 'sampleNames', 'subsetBySamples', 'subsetByColumns'
- define subsetByRows, subsetByRanges for RangedBT
- establish a tiling of a chromosome using GenomicRanges::tileGenome and
get performance on traversal of a chromosome, compare to Bioconductor
with yriMulti package
